% Professional CV - Single Page Optimized
\documentclass[10pt,a4paper]{article}

% Essential packages
\usepackage[top=0.5cm, bottom=0.45cm, left=1.0cm, right=1.0cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{microtype}
\usepackage{fontawesome5}
\usepackage{tikz}
\usepackage{tcolorbox}

% Use modern font
\usepackage[defaultsans,scale=0.95]{opensans}
\renewcommand\familydefault{\sfdefault}
\linespread{1.12}

% Define color palette
\definecolor{primary}{RGB}{30, 50, 100}
\definecolor{secondary}{RGB}{0, 128, 128}
\definecolor{text}{RGB}{52, 52, 52}
\definecolor{lightgray}{RGB}{240, 240, 240}
\definecolor{darkgray}{RGB}{80, 80, 80}

% Setup hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=secondary,
    urlcolor=secondary,
    pdftitle={Ha Van Dung - Resume}
}

% Customize section titles
\titleformat{\section}
    {\fontsize{12}{14}\bfseries\color{primary}}
    {}{0em}
    {}
    [{\color{lightgray}\titlerule[0.5pt]}]
\titlespacing{\section}{0pt}{8pt}{5pt}

% Custom commands
\newcommand{\contactinfo}[3]{
    \makebox[0pt][l]{\textcolor{secondary}{#1}}%
    \hspace{16pt}\href{#2}{#3}
}

\newcommand{\projectitem}[5]{
    \noindent\begin{tcolorbox}[
        colback=white,
        colframe=lightgray,
        boxrule=0.3pt,
        arc=2pt,
        top=3pt,
        bottom=3pt,
        left=6pt,
        right=6pt
    ]
        \noindent\textbf{\color{primary}#1} \hfill \textcolor{darkgray}{\scriptsize#2}\\[1pt]
        {\small\color{secondary}#3}\\[1pt]
        {\scriptsize\color{darkgray}#4}\\[3pt]
        #5
    \end{tcolorbox}
}

% Begin document
\begin{document}
\pagestyle{empty}

% Header Section
\begin{center}
    \textbf{\fontsize{22}{26}\selectfont\color{primary}HA VAN DUNG}\\[2pt]
    \textcolor{secondary}{\normalsize Fullstack Developer}\\[6pt]
    
    % Contact Information
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{}}
        \contactinfo{\faPhone}{tel:+84327250461}{+84 32 725 0461} &
        \contactinfo{\faEnvelope}{mailto:dungken2211@gmail.com}{dungken2211@gmail.com} &
        \contactinfo{\faGlobe}{}{Thu Duc, HCMC} \\[3pt]
        \contactinfo{\faLinkedin}{https://linkedin.com/in/dungdev}{linkedin.com/in/dungdev} &
        \contactinfo{\faGithub}{https://github.com/dungken}{github.com/dungken} &
        \contactinfo{\faYoutube}{https://youtube.com/@dungkenn}{youtube.com/@dungkenn}
    \end{tabular*}
\end{center}

\vspace{2pt}
\hrule height 0.3pt
\vspace{6pt}

% Professional Summary
\section{PROFESSIONAL SUMMARY}
\color{text}\small
Experienced fullstack developer with a strong foundation in modern web and mobile technologies. Specialized in building scalable applications with clean architecture, payment integrations, and real-time features. Passionate about creating efficient solutions that solve real-world problems through innovative technology.

\vspace{6pt}

% Project Experience
\section{PROJECT EXPERIENCE}

\projectitem{VinCharge Subscription Platform (Real-world client project) }{Mar 2025 -- Present}
    {Java 17 • Spring Boot 3.2 • PostgreSQL • VNPay • JWT • Cloudinary}
    {\href{https://github.com/dungken}{\textcolor{secondary}{\faGithub* GitHub}} | \href{YOUR_YOUTUBE_DEMO_LINK}{\textcolor{secondary}{\faYoutube* Demo}}}
    {\begin{itemize}[leftmargin=12pt,itemsep=1pt,parsep=0pt,topsep=0pt,after=\vspace{-2pt},label={•}]
        \item Enterprise EV charging subscription management system for VinFast with complete billing cycle.
        \item Integrated VNPay payment gateway with HMAC-SHA512 encryption and IPN handling.
        \item Implemented JWT authentication with refresh tokens and OTP-based password recovery.
        \item Designed optimized PostgreSQL schema with Flyway migrations and audit fields.
        \item Built layered REST architecture with OpenAPI documentation and global exception handling.
        \item Automated email notifications via Gmail SMTP and Cloudinary for meter reading storage.
    \end{itemize}}

\vspace{3pt}

\projectitem{Speaking English with AI (Collaborative project with a team of 4 developers) }{Feb 2025 -- May 2025}
    {Flutter • Dart • BLoC • Clean Architecture • Hive • Speech Recognition}
    {\href{https://github.com/dungken}{\textcolor{secondary}{\faGithub* GitHub}} | \href{YOUR_YOUTUBE_DEMO_LINK}{\textcolor{secondary}{\faYoutube* Demo}}}
    {\begin{itemize}[leftmargin=12pt,itemsep=1pt,parsep=0pt,topsep=0pt,after=\vspace{-2pt},label={•}]
        \item Cross-platform language learning app with AI-powered conversation practice and feedback.
        \item Architected scalable Clean Architecture with BLoC pattern and repository interfaces.
        \item Optimized audio recording with SurfaceView lifecycle management and buffer queue control.
        \item Integrated speech-to-text with AI-driven feedback on pronunciation, grammar, and fluency.
        \item Designed feature-first architecture with comprehensive dependency injection.
        \item Built responsive UI with adaptive layouts and progress tracking analytics.
    \end{itemize}}

\vspace{3pt}

\projectitem{Trello Clone - Project Management (Solo development project) }{Jan 2025 -- Apr 2025}
    {Node.js • Express • MongoDB • Socket.IO • JWT • Cloudinary • Brevo}
    {\href{https://github.com/dungken}{\textcolor{secondary}{\faGithub* GitHub}} | \href{YOUR_YOUTUBE_DEMO_LINK}{\textcolor{secondary}{\faYoutube* Demo}}}
    {\begin{itemize}[leftmargin=12pt,itemsep=1pt,parsep=0pt,topsep=0pt,after=\vspace{-2pt},label={•}]
        \item Full-featured kanban board with real-time collaboration via Socket.IO for agile project management.
        \item Designed RESTful API with Express.js following MVC architecture and versioned endpoints.
        \item Implemented JWT authentication with refresh tokens, cookie storage, and route protection.
        \item Developed complex MongoDB aggregation pipelines with pagination and filtering.
        \item Integrated Cloudinary for file attachments and Brevo for automated email notifications.
        \item Created advanced invitation system with role-based access control and board sharing.
    \end{itemize}}

\vspace{6pt}

% Additional Sections
\section{EDUCATION}
\noindent\textbf{Bachelor of Science in Information Technology} \hfill \textcolor{darkgray}{\small 2022 -- 2026}\\[1pt]
\textcolor{darkgray}{\small University of Transport and Communications, Ho Chi Minh City}

\vspace{6pt}

\section{CERTIFICATIONS \& ACHIEVEMENTS}
\begin{minipage}[t]{0.5\textwidth}
    \textbf{\small International Collegiate Programming Contest}\\[1pt]
    \href{https://github.com/dungken/MyResume/blob/master/Certificates/icpc.png}{\textcolor{secondary}{\scriptsize View Certificate}}
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
    \textbf{\small Scientific Research Certificate}\\[1pt]
    \href{https://github.com/dungken/MyResume/blob/master/Certificates/nckh.png}{\textcolor{secondary}{\scriptsize View Certificate}}
\end{minipage}

\vspace{4pt}

\begin{minipage}[t]{0.5\textwidth}
    \textbf{\small Leetcode Top Interview 150 - YouTube Series} \hfill \textcolor{darkgray}\\[1pt]
    \href{https://www.youtube.com/playlist?list=PLE9QkkVvuT1kc_pgqSPTvgggPg37ZHA6V}{\textcolor{secondary}{\scriptsize Watch Series}}
\end{minipage}%

\vspace{6pt}

\section{LANGUAGES}
\textbf{\color{darkgray}\small Vietnamese:} \textcolor{text}{\small Native} \hspace{15pt} \textbf{\color{darkgray}\small English:} \textcolor{text}{\small  Able to use in professional and technical work environments }

\end{document}